\documentclass[10pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.95]{geometry}
\usepackage{comment}
\usepackage{xspace}
\usepackage{pdfpages}
\usepackage{pgf, tikz}
\usepackage{color}

\name{Alex Hermann}{SOCKENG KOUSSOK}
%\photo[80pt][0.0pt]{Hsock.jpg}
\title{Data Analyst | Engineer in Applied Mathematics}
%\title{Mathematical Modeling and Scientific Computing Expert}
\address{}{Ngoa-ekele Yaounde, Cameroon}{}
\phone[mobile]{+237~690~21~87~96}
\email{hsockeng@yahoo.com}
\social[linkedin][www.linkedin.com/in/hermann-sockeng-1a29571a9/]{Hermann Sockeng In}
\social[github]{Hermann-Sockeng}
\social[twitter]{HermannSockeng}
\extrainfo{30 years old, single}
%. \\ \textbf{References Name}\\ Jean-Jules TEWA\\ tewajules@gmail.com\\ Joseph MBANG\\ mbangjoseph74@gmail.com
\quote{Data-driven Engineer in Applied Mathematics skilled in computational tools, mathematical modeling, and advanced analytics. Experienced in data preprocessing, EDA, predictive modeling, and data visualization. Committed to continuous learning and delivering tangible results. Seeking a challenging role to apply expertise in solving complex business problems through data-driven strategies.}
%\quote{In mathematics, beauty is not just about a pretty equation; it's about elegant solutions that unlock the secrets of the universe.}
\begin{document}	
\makecvtitle	
\section{Education}
	\cventry{2020--2021}{Master of philosophy in Mathematical Modeling \& Scientific Computing}{National Advanced School of Engineering, Polytechnic, University of Yaounde 1}{Yaounde, Cameroon}{\textit{GPA: 3.15/4}}{Completed coursework focused on utilizing computational tools for data analysis, algorithm development, and mathematical simulations. Overall, the degree provided a comprehensive understanding of applied mathematics principles and their practical applications, equipping me with the knowledge and skills to tackle complex problems in various industries. }
	\cventry{2017--2018}{Bachelor of Science in Mathematics \& Computer Science}{Faculty of science, University of Yaounde 1}{Yaounde, Cameroon}{\textit{GPA: 2.15/4.00}}{Completed coursework focused on  Calculus, Linear Algebra, Probability and Statistics, Discrete Mathematics, Algorithms and Data Structures, Computer Programming, and Operating Systems.}
	\section{Experience}
\subsection{Work}
\cventry{2023--Present}{Lecturer}{INSTITUT UNIVERSITAIRE MATAMFEN}{Yaounde, Cameroon}{}{Instructor in mathematical analysis, numerical methods, statistics, and data analysis for two-year technical students. Equipping students with essential analytical skills for data-driven decision-making and quantitative management.}
	\subsection{Internships}
	\cventry{Sept, 2023--Present}{Research engineer in BigData \& AI development}{BENSEARCH SOLUTIONS SAS}{Paris, 30 Rue de la Grande Île Meaux, France (\textbf{Hybrid})}{}{Led creation of client database for Bensearch Solutions SAS, utilizing advanced data processing techniques and machine learning to extract actionable insights. Strong expertise in SQL server, NoSQL databases, and data-driven decision making.}

%	\cventry{2022--Present}{Partial Lecturer}{\'Ecole Privée de Radiologie et D'imagérie Médicale Dorcas}{Yaounde, Cameroon}{}{Courses: Applied Mathematics}


%	\cventry{2020}{Data Analyst}{MEGASOFT SARL}{Yaounde, Cameroon}{}{}
%	\cvitem{Topic \& Ref}{Analysis of personnel profiles and results. \; Ref: Direction: imoukouop@gmail.com}
%	\cvitem{Keywords}{Data collection, EDA, PCA, Semi-supervised regression, Semi-supervised classification.}
		
				\cventry{Jun 2020 - Sep 2020 }{Data Analyst}{MEGASOFT SARL}{Yaounde}{}{As a data analyst, I led a project where we collected and curated the data to predict the technical and psychological aptitude of candidates following a recruitment test. By identifying key factors influencing the outcomes, we optimized the recruitment process and made informed decisions regarding candidate selection.}
%	\cventry{2021}{--Master's thesis}{Mathematical Engineering and Information Systems Lab}{Cameroon}{}{}
%	\cvitem{Topic}{Semi-supervised clustering with constraints. \; Supervisor: Dr. Wilson TOUSSILE}
%	\cvitem{Keywords}{Clustering, Semi-supervised learning, Hidden Markov Model, EM type algorithm.}
	
	\section{Skills}	
	\cvitem{}{
		\begin{minipage}[t]{0.45\textwidth}
			\begin{itemize}
				\item Mathematical Modeling
				\item Data Analysis: preprocessing, EDA, statistical analysis
				\item Programming: Python, R, MATLAB, Fortran, SQL
				\item Data visualization
				\item English (Professional working proficiency)
			\end{itemize}
		\end{minipage}
		\hfill
		\begin{minipage}[t]{0.45\textwidth}
			\begin{itemize}
				\item Predictive Modeling: machine learning algorithms
				\item Optimization
				\item Statistical Analysis
				\item Communication and Continuous Learning
				\item French (Native - Fluent)
			\end{itemize}
		\end{minipage}
	}
	
	\begin{comment}
		
	
	\cvitem{Technical}{	Numerical analysis and modeling,
		Algorithm development and optimization,
		Data analysis and visualization,
		Data Storytelling,
		Predictive modeling and machine learning,
		Problem-solving and critical thinking,
		Communication and teamwork, Python, R, MatLab, Fortran, SQL, NoSQL, LaTeX}
	\cvitem{Languages}{English (Professional working proficiency), French (Native - Fluent)}
	
	\end{comment}
	\section{GitHub projects}
%	\cvitem{}{List any relevant publications or research projects}
	\cventry{HR Project}{Python App for HR}{to predict a candidate's technical skills, psychological aptitude, and job sustainability based on their recruitment test results in conjunction with HR department of MEGASOFT}{}{}{}
	\cventry{Article draft}{Morpho-syntax labelling Python App}{to detect automatically an Anaphora pronominal adverbial and the antecedent in a German language text in collaboration with a PhD student in computational linguistic.}{}{}{}
\section{Certificates}
%\definecolor{links}{HTML}{2A1B81}
%\hypersetup{urlcolor=links}
\cventry{2023}{\href{https://www.credly.com/badges/d4e6d231-c219-4fd1-9567-470ffb744a58/linked_in_profile}{IBM Data Analyst Professional Certificate}}{Coursera}{}{}{}
\cventry{Sep $1^{st}$, 2023}{\href{https://www.credly.com/badges/4d09b5bc-10cb-46cc-837c-bdfdee9300ab/linked_in_profile}{IBM Data Science Professional Certificate}}{Coursera}{}{}{}
\cventry{Feb 21, 2023}{\href{https://www.credly.com/badges/5faf0150-6b30-46b1-8a04-abe2e5bad292/public_url}{Applied Data Science Lab}}{WorldQuant University}{\href{https://www.wqu.edu/programs/applied-ds-lab/}{ New Orleans, United States.}}{}{}
\cventry{Sep 30, 2022}{\href{https://coursera.org/share/2bab9998f8f6439aaca49ed650e9615c}{Artificial Intelligence for Medicine Specialization}}{Coursera}{}{}{}
%	\cvitem{}{Include any other relevant information, such as certifications or awards}
%	\cventry{Sep 04, 2023}{Intermediate English Courses}{World English Institute}{Reading, Listen and Writing}{}{}
%\includepdf[pages=-]{Malaria Modeling Research Proposal.pdf}	
%	\includepdf[pages=-]{Master Scientific Computing.pdf}
\end{document}